\documentclass[10.5pt,letterpaper]{article}

\usepackage[top=0.55in, bottom=0.5in, left=0.6in, right=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\newcommand{\pipe}{$\quad \mid \quad$}
\hypersetup{colorlinks=false, hidelinks}

% No page numbers
\pagestyle{empty}

% Section formatting: bold, all caps, full-width rule below
\titleformat{\section}
  {\normalfont\bfseries\normalsize}
  {}{0em}
  {\MakeUppercase}
  [\vspace{-4pt}\rule{\linewidth}{0.6pt}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Tight lists
\setlist[itemize]{leftmargin=1.6em, itemsep=1pt, topsep=2pt, parsep=0pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$}
%\setlist[itemize]{topsep=2pt, itemsep=3pt, parsep=0pt, partopsep=0pt}

% No paragraph indent
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Helper: right-aligned date on same line
\newcommand{\entrytitle}[2]{%
  \textbf{#1}\hfill #2%
}
\newcommand{\entrysub}[2]{%
  \vspace{1pt}\textit{#1}\hfill \textit{#2}%
}

% Tighten section spacing
\titlespacing*{\section}{0pt}{6pt}{4pt}
%
\begin{document}

%% ── HEADER ──────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Md Shaifur Rahman}\\[4pt]
  Seattle, WA 98115 \pipe{} 
  \href{mailto:mdshaifur@protonmail.com}{mdshaifur@protonmail.com} \pipe{}
  917-701-0637 \pipe{} \href{https://linkedin.com/in/mdshaifur}{linkedin.com/in/mdshaifur}\\[2pt]
  \href{https://github.com/shaifurcodes}{github.com/shaifurcodes}\pipe{} 
  \href{https://dev.to/shaifurcodes}{dev.to/shaifurcodes}\pipe{} 
  \href{https://plasso.ai}{plasso.ai}\pipe{} 
  \href{https://plasso.ai/portfolio}{plasso.ai/portfolio}
\end{center}

\vspace{2pt}

%% ── SUMMARY ─────────────────────────────────────────────────────────────────
\section*{Summary}
Computer Science PhD (2025) and startup founder with a strong systems R\&D background and 4 granted US patents that directly contributed to securing seed funding. Proven expertise engineering end-to-end intelligent systems, bridging low-level firmware and RTOS with real-time software stacks and hardware-accelerated ML inference on resource-constrained hardware. Leveraged this full-stack depth to architect the core infrastructure and AI stack powering Plasso (plasso.ai) --- bringing embodied AI from research to production.

%% ── TECHNICAL SKILLS ────────────────────────────────────────────────────────
\section*{Technical Skills}
{\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{@{}p{0.22\textwidth}>{\arraybackslash\raggedright}X@{}}

\textbf{Robotics \& Autonomy:} & ROS 2, Nav2, MoveIt 2, Trajectory Optimization, Gazebo, Isaac Sim, MuJoCo Playground, URDF, BehaviorTree.CPP, OpenCV, Depth Estimation, PCL, LiDAR SLAM, EKF, UKF, IMU, Sensor Fusion, Wheel Odometry \tabularnewline

\textbf{Embodied AI \& ML:} & VLA, VLM, 3D Object Detection, Edge LLM Deployment, Gemma, SmolVLA, Llama.cpp, TensorRT, ONNX, ONNX Runtime, LeRobot, Imitation Learning, Reinforcement Learning, PyTorch, Hugging Face \tabularnewline

\textbf{Embedded \& Systems:} & C, C++, Python, Zephyr, FreeRTOS, Low-Level Firmware, PID, Latency Optimization, Linux, SPI, I2C, UART, CAN Bus \tabularnewline

\textbf{HW \& Edge Compute:} & NVIDIA Jetson Orin Nano, Jetson AGX, CUDA, 6-DOF SO-101 Robotic Arm, KiCad, RPLIDAR C1, IMX219 Cameras, Mobile Robot Power Systems \tabularnewline

\textbf{DevOps \& Tooling:} & FreeCAD, OpenSCAD, CI/CD, GitHub Actions, Hardware-in-the-Loop, Regression Testing, Docker \tabularnewline

\end{tabularx}}


%% ── EXPERIENCE ──────────────────────────────────────────────────────────────
\section{Professional Experience}
\entrytitle{Plasso (\href{https://plasso.ai}{plasso.ai})}{Seattle, WA}\\
\entrysub{Founder \& CEO}{May 2026 -- Present}
\begin{itemize}
    \item Architected an end-to-end embodied AI robotics platform as sole founder, executing full-lifecycle hardware/software co-design across mechanical assemblies, custom PCBs in KiCad, and low-level firmware in C/C++.
    \item Engineered a fully offline, zero-cloud-dependency edge AI stack on NVIDIA Jetson devices: local LLM inference via llama.cpp, RAG-based context retrieval, and imitation/reinforcement learning pipelines via Hugging Face for physical behavior training.
    \item Developed a production-grade real-time software stack with strict node lifecycle management, BehaviorTree.CPP for task orchestration, and automated CI/CD pipelines via GitHub Actions.
    \item Designed autonomous mobility architecture implementing multi-sensor fusion across LiDAR, IMU, wheel odometry, and stereo vision for indoor SLAM and navigation.
\end{itemize}
%
\vspace{2pt}
%
\entrytitle{NEC Labs America}{Princeton, NJ}\\
\entrysub{Research Intern --- Embedded Systems \& Localization}{Jun 2019 -- Apr 2021}
\begin{itemize}
    \item Led firmware and core algorithm development for NavigateIO, a zero-infrastructure 3D tracking platform for first responders, fusing UWB, IMU, LoRa, and visual odometry on ARM Cortex-M microcontrollers.
    \item Achieved sub-meter 3D positioning accuracy in multi-story NLOS environments using Qorvo/Decawave DW1000 UWB transceivers; novel drop-and-go anchor architecture enables deployment in under 60 seconds.
    \item Architected a resilient end-to-end embedded IoT stack with low-level sensor drivers (SPI, I2C, UART), real-time high-throughput data pipelines, and fault-tolerant system diagnostics.
    \item Co-invented 4 granted US patents (12,335,899 $\cdot$ 12,207,226 $\cdot$ 11,595,934 $\cdot$ 11,388,564) covering infrastructure-free RF tracking architectures, directly contributing to securing \$1M in seed capital.
\end{itemize}
%
\vspace{2pt}
%
\entrytitle{Stony Brook University --- Wireless \& Networks Lab}{Stony Brook, NY}\\
\entrysub{Research Assistant (NSF-funded)}{May 2014 -- May 2025}
\begin{itemize}
    \item \textbf{FSO-VR} (NSF \#1815306, \$500K): Designed and prototyped a steerable Free Space Optics wireless link for AR/VR headsets using Galvo-mirror beam steering and real-time RSSI feedback; achieved 99.99\% link availability at 8K VR bandwidth; led to a US patent.
    \item \textbf{FSONet} (NSF \#1514017, \$720K): Built a 100m FSO backhaul prototype with custom tracking and pointing mechanism; validated resilience against fog and vibration; formulated near-optimal transceiver placement algorithm for 3D urban topologies; published at ACM MobiCom 2017.
    \item \textbf{SpecSense} (NSF \#1642965, \$800K): Developed crowdsensed spectrum occupancy mapping using RTL-SDRs and spatial interpolation; designed temporal clustering for time-varying maps; published at IEEE INFOCOM 2017.
\end{itemize}
%
\vspace{2pt}
%
\entrytitle{Stony Brook University}{Stony Brook, NY}\\
\entrysub{Teaching Assistant}{Aug 2013 -- May 2014}
\begin{itemize}
    \item Guided students in Software Development, Theory of Database Systems, and Wireless \& Mobile Networks; provided mentorship and project supervision.
\end{itemize}
%
\vspace{2pt}
%
\entrytitle{Philips Research North America}{Briarcliff, NY}\\
\entrysub{Research Intern --- IoT}{Jun 2015 -- Aug 2015}
\begin{itemize}
    \item Integrated the open-source OpenAirInterface (OAI) EPC stack to encapsulate and route high-density smart city street lighting data over LTE network infrastructure.
\end{itemize}
%
\vspace{2pt}
%
\entrytitle{Bangladesh University of Engineering and Technology}{Dhaka, Bangladesh}\\
\entrysub{Lecturer, Computer Science}{May 2009 -- Jun 2013}
\begin{itemize}
    \item Delivered courses on VLSI Design, AI, Theory of Computation, Operating Systems, Database Systems, and Microprocessor Design; served as Cisco CCNA 1--4 Trainer.
    \item Consulted on the Central Bank of Bangladesh automation project and Bangladesh's first machine-readable passport system.
\end{itemize}

%% ── EDUCATION ───────────────────────────────────────────────────────────────
\section{Education}

\entrytitle{Stony Brook University}{Stony Brook, NY}\\
\entrysub{Ph.D., Computer Science}{May 2025}
\begin{itemize}
  \item Dissertation: ``License-free Use of RF and Infrared Spectrum'' ---
        Advisors: Prof.\ Himanshu Gupta \& Prof.\ Samir Das
  \item Dept.\ Fellowship (2013--2014); ACM SIGCOMM, MobiSys \& IEEE SMARTCOMP Travel Grant recipient
\end{itemize}

\vspace{2pt}
\entrytitle{Stony Brook University}{Stony Brook, NY}\\
\entrysub{M.S., Computer Science\ \ ---\ \ GPA 3.78/4.0}{Dec 2017}

\vspace{2pt}
\entrytitle{Bangladesh University of Engineering and Technology}{Dhaka, Bangladesh}\\
\entrysub{B.S., Computer Science\ \ ---\ \ GPA 3.92/4.0\ \ (Dean's List every semester)}{Mar 2009}
%
%% ── PATENTS ──────────────────────────────────────────────────────────────
\section{US Patents}
US 12,335,899 $\cdot$ US 12,207,226 $\cdot$ US 11,595,934 $\cdot$ US 11,388,564 --- Infrastructure-free RF tracking and localization system for first responders (NavigateIO).
%
%% ── PUBLICATIONS ────────────────────────────────────────────────────────────
\section{Selected Publications}
\textit{200+ citations, h-index 7 -- Google Scholar: https://tinyurl.com/296y5zw2}
%
\begin{enumerate}[leftmargin=1.6em, itemsep=1pt, topsep=2pt, parsep=0pt]
  \item \textbf{Rahman} et al. ``DynoLoc: Infrastructure-free RF Tracking in Dynamic Indoor Environments.'' \textit{Under revision, IEEE Trans.\ Mobile Computing}, 2026.
  \item \textbf{Rahman} et al. ``FSONet: A Wireless Backhaul for Multi-Gigabit Picocells Using Steerable FSO.'' \textit{ACM MobiCom}, 2017.
  \item \textbf{Rahman} et al. ``SpecSense: Crowdsensing for Efficient Querying of Spectrum Occupancy.'' \textit{IEEE INFOCOM}, 2017.
  \item \textbf{Rahman} et al. ``FSO-VR: Steerable Free Space Optics Link for Virtual Reality Headsets.'' \textit{ACM WearSys}, 2018.
  \item Curran, \textbf{Rahman} et al. ``Rethinking Virtual Network Embedding in Reconfigurable Networks.'' \textit{IEEE SECON}, 2018.
  \item Gupta, \textbf{Rahman}, Curran. ``Spectrum Allocation via Pathloss Estimation in Crowdsensed Shared Spectrum Systems.'' \textit{IEEE DySPAN}, 2019.
  \item \textbf{Rahman} et al. ``Creating Spatio-temporal Spectrum Maps from Sparse Crowdsensed Data.'' \textit{IEEE WCNC}, 2019.
  \item \textbf{Rahman}, Naznin. ``Efficient Routing in a Sensor Network Using Collaborative Ants.'' \textit{Springer ICSI}, 2016.
\end{enumerate}
%
%% ── PROJECTS ──────────────────────────────────────────────────────────────
\section{Projects}

\entrytitle{Praxis --- Open-Source Robotics Learning Platform}{\href{https://github.com/shaifurcodes/praxis-robotics}{github.com/shaifurcodes/praxis-robotics}}
\begin{itemize}
    \item Built a fully integrated zero-cloud-dependency LLM/VLA/VLM-enabled mobile manipulation platform: Yahboom 2WD chassis with 520 DC motors, LeRobot SO-101 arm with wrist camera, dual IMX219 front cameras, LiDAR, and Yahboom 10-axis IMU --- all interfaced to NVIDIA Jetson Orin Nano Super 8GB.
    \item Implemented end-to-end task execution pipeline: voice commands via Bluetooth parsed by a local Gemma 4 E2B LLM, action grounding via SmolVLA, OpenCV-based object detection, LiDAR SLAM for mobility, and imitation/RL-trained arm control for pick-and-place.
\end{itemize}
\end{document}
